Unshuffling Permutations

### 2016-02-10 submission.tex
Small chages

Let us now provide some definitions about graphs and oriented perfect 
matchings that are used in the sequel. If $G$ is an oriented graph 
without loops, two different edges of $G$ are {\em independent} if they 
do not share any common vertex. We say that $G$ is an 
{\em oriented matching} if all edges of $G$ are pairwise independent. 
Moreover, $G$ is {\em perfect} if all vertices of $G$ belong to at least 
one arc. For any word $u = u_1 u_2 \dots u_n$, an 
{\em oriented perfect matching on $u$} is an oriented perfect matching 
$\mathcal{M}$ on the set of vertices $\{u_1, u_2, \dots, u_n\}$. In the 
sequel, we shall consider a natural notion of pattern avoidance in 
oriented perfect matchings on words. For instance, an oriented perfect
matching $\mathcal{M}$ of a word $u$ {\em admits an occurrence} of the 
pattern $\CrossingRL$ if there are four positions $i < j < k < \ell$ in 
$u$ such that $(u_k, u_i)$ and $(u_j, u_\ell)$ are arcs of $\mathcal{M}$. 
When $\mathcal{M}$ does not admit any occurrence of a pattern 
$\mathcal{P}$, we say that $\mathcal{M}$ {\em avoids}~$\mathcal{P}$.

@@

\begin{definition}[Property $\mathbf{P_1}$]
  \label{definition:Property P_1}
  Let $\pi$ be a permutation. An oriented perfect matching $\mathcal{M}$
  on $\pi$ is said to have property $\mathbf{P_1}$ if it avoids the 
  patterns \InclusionLL, \InclusionLR, \InclusionRL, 
  \InclusionRR, \CrossingLR, and \CrossingRL.
\end{definition}

>>>>

Let us now provide some definitions about graphs and oriented perfect 
matchings that are used in the sequel. If $G$ is an oriented graph 
without loops, two different edges of $G$ are {\em independent} if they 
do not share any common vertex. We say that $G$ is an 
{\em oriented matching} if all edges of $G$ are pairwise independent. 
Moreover, $G$ is {\em perfect} if any vertex of $G$ belongs to at least 
one arc. For any word $u = u_1 u_2 \dots u_n$, an 
{\em oriented perfect matching on $u$} is an oriented perfect matching 
$\mathcal{M}$ on the set of vertices $\{u_1, u_2, \dots, u_n\}$. In the 
sequel, we shall consider a natural notion of pattern avoidance in 
oriented perfect matchings on words. For instance, an oriented perfect
matching $\mathcal{M}$ on a word $u$ {\em admits an occurrence} of the 
pattern $\CrossingRL$ if there are four positions $i < j < k < \ell$ in 
$u$ such that $(u_k, u_i)$ and $(u_j, u_\ell)$ are arcs of $\mathcal{M}$. 
When $\mathcal{M}$ does not admit any occurrence of a pattern 
$\mathcal{P}$, we say that $\mathcal{M}$ {\em avoids}~$\mathcal{P}$.

@@

\begin{definition}[Property $\mathbf{P_1}$]
  \label{definition:Property P_1}
  Let $\pi$ be a permutation. An oriented perfect matching $\mathcal{M}$
  on $\pi$ is said to have property $\mathbf{P_1}$ if it avoids all the 
  six patterns \InclusionLL, \InclusionLR, \InclusionRL, 
  \InclusionRR, \CrossingLR, and \CrossingRL.
\end{definition}
